---
title: The data classes
author: R package build
date: '2022-02-23'
slug: the-data-classes
categories: []
tags: []
---
# Set up Information

```{r}
library(tidyverse)
library(lubridate)
cat_lovers <- read_csv("https://raw.githubusercontent.com/Burgosa2020/tidyverse/main/cat-lovers.csv")
url<- 'https://raw.githubusercontent.com/Burgosa2020/tidyverse/main/hotels.csv'
hotels <- read_csv(url)

```

# Factors
R uses factors to handle categorical variables, variables that have a fixed and known set of possible values
```{r}
x <- factor(c("BS", "MS", "PhD", "MS"))
x
```

```{r}
typeof(x)
```
```{r}
class(x)
```

```{r}
glimpse(x)
```
```{r}
as.integer(x)
```
## Dates

```{r}
y <- as.Date("2022-02-12")
y
```
```{r}
typeof(y)
```
```{r}
class(y)
```
**More Data** 
We can think of dates like an integer (the number of days since the origin, 1 Jan 1970) and an integer (the origin) glued together

```{r}
as.integer(y)
```
```{r}
as.integer(y) / 365 # roughly 50 yrs
```
**Data Frame**
We can think of data frames like like vectors of equal length glued together
```{r}
df <- data.frame(x = 1:2, y = 3:4)
df
```
```{r}
typeof(df)
class(df)
```
### Manipulate factors
**lubridate** is the tidyverse-friendly package that makes dealing with dates a little easier
```{r}
cat_lovers %>%
  mutate(handedness = fct_infreq(handedness)) %>%
  ggplot(mapping = aes(x = handedness)) +
  geom_bar()
```

## Working with Dates

```{r}
hotels %>%
  select(starts_with("arrival_"))
```

### Step 1. Construct Dates

```{r}
library(glue)
hotels %>%
  mutate(
    arrival_date = glue("{arrival_date_year} {arrival_date_month} {arrival_date_day_of_month}")
    ) %>% 
  relocate(arrival_date)
```
### Step 2. Count Booking Per Date

```{r}
hotels %>%
  mutate(arrival_date = glue("{arrival_date_year} {arrival_date_month} {arrival_date_day_of_month}")) %>%
  count(arrival_date)
```

### Step 3. Visualise Booking Per Date

```{r}
hotels %>%
  mutate(arrival_date = glue("{arrival_date_year} {arrival_date_month} {arrival_date_day_of_month}")) %>%
  count(arrival_date) %>%
  ggplot(aes(x = arrival_date, y = n, group = 1)) +
  geom_line()
```

## More Percise


### Step 1. *Revised* Contruct dates "as dates"
```{r}
library(lubridate)
hotels %>%
  mutate(
    arrival_date = ymd(glue("{arrival_date_year} {arrival_date_month} {arrival_date_day_of_month}"))
    ) %>% 
  relocate(arrival_date)
```

## Step 2.  Count Booking Per Date
```{r}
hotels %>%
  mutate(arrival_date = ymd(glue("{arrival_date_year} {arrival_date_month} {arrival_date_day_of_month}"))) %>% 
  count(arrival_date)

```

### Step 3a.  Visualise Booking Per Date

```{r}
hotels %>%
  mutate(arrival_date = ymd(glue("{arrival_date_year} {arrival_date_month} {arrival_date_day_of_month}"))) %>% 
  count(arrival_date) %>%
  ggplot(aes(x = arrival_date, y = n, group = 1)) +
  geom_line()
```

### Step 3b.  Visualise Using a Smooth Curve

```{r}
hotels %>%
  mutate(arrival_date = ymd(glue("{arrival_date_year} {arrival_date_month} {arrival_date_day_of_month}"))) %>% 
  count(arrival_date) %>%
  ggplot(aes(x = arrival_date, y = n, group = 1)) +
  geom_smooth()
```










