---
title: Data Type
author: R package build
date: '2022-02-21'
slug: data-type
categories: []
tags: []
---
```{r}
library(tidyverse)
cat_lovers <- read_csv("https://raw.githubusercontent.com/Burgosa2020/tidyverse/main/cat-lovers.csv")
cat_lovers %>%
  summarise(mean_cats = mean(number_of_cats))
```
```{r}
?mean
```
```{r}
View(cat_lovers)
```
```{r}
cat_lovers %>%
  mutate(number_of_cats = case_when(
    name == "Ginger Clark" ~ 2,
    name == "Doug Bass"    ~ 3,
    TRUE                   ~ as.numeric(number_of_cats)
    )) %>%
  summarise(mean_cats = mean(number_of_cats))
```
```{r}
cat_lovers %>%
  mutate(
    number_of_cats = case_when(
      name == "Ginger Clark" ~ "2",
      name == "Doug Bass"    ~ "3",
      TRUE                   ~ number_of_cats
      ),
    number_of_cats = as.numeric(number_of_cats)
    ) %>%
  summarise(mean_cats = mean(number_of_cats))

```

```{r}
cat_lovers <- cat_lovers %>%
  mutate(
    number_of_cats = case_when(
      name == "Ginger Clark" ~ "2",
      name == "Doug Bass"    ~ "3",
      TRUE                   ~ number_of_cats
      ),
    number_of_cats = as.numeric(number_of_cats)
    )
```
## Logical and charcter 
```{r}
typeof(TRUE)
typeof("hello")
```
### Double and Interger

*double* - floating point numerical values (default numerical type)
```{r}
typeof(1.335)
typeof(7)

```

*integer* - integer numerical values (indicated with an L)
```{r}
typeof(7L)
typeof(1:3)

```
## Concatenation
Vectors can be constructed using the c() function.

```{r}
c(1, 2, 3)
c("Hello", "World!")
c(c("hi", "hello"), c("bye", "jello"))

```

### Converting between types
```{r}
x <- 1:3
x
typeof(x)
```
```{r}
y <- as.character(x)
y
typeof(y)
```
# Special Values

**NA**: Not available

**NaN**: Not a number

**Inf**: Positive infinity

**-Inf**: Negative infinity
```{r}
pi / 0
```
```{r}
1/0 - 1/0
```
```{r}
1/0 + 1/0
```
```{r}
0 / 0
```

```{r}
x <- c(1, 2, 3, 4, NA)
mean(x)
mean(x, na.rm = TRUE)
summary(x)
```
```{r}
typeof(NA)
```
# Mental Model Types
```{r}
# TRUE or NA
TRUE | NA
```
```{r}
# FALSE or NA
FALSE | NA
```
**NA** is unknown, so it could be TRUE or FALSE
```{r}
TRUE | TRUE  # if NA was TRUE
```
```{r}
FALSE | TRUE  # if NA was TRUE
```
```{r}
TRUE | FALSE # if NA was FALSE
```
```{r}
FALSE | FALSE # if NA was FALSE
```
Doesn't make sense for mathematical operations

Makes sense in the context of missing data






















