---
title: Data IO
author: R package build
date: '2022-02-23'
slug: data-io
categories: []
tags: []
---
# Readr
```{r}
library(tidyverse)
```

```{r}
nobel <- read.csv(file = "https://raw.githubusercontent.com/Burgosa2020/tidyverse/main/nobel.csv")
nobel

```
```{r}
df <- tribble(
  ~x, ~y,
  1,  "a",
  2,  "b",
  3,  "c"
)
write_csv(df, file = "https://raw.githubusercontent.com/Burgosa2020/tidyverse/main/df.csv")
read.csv("https://raw.githubusercontent.com/Burgosa2020/tidyverse/main/df.csv")

```
## Variable Names

```{r}
edibnb_badnames <- read.csv("https://raw.githubusercontent.com/Burgosa2020/tidyverse/main/edibnb-badnames.csv")
names(edibnb_badnames)

```
## Defining Column Names

```{r}
edibnb_col_names <- read_csv("https://raw.githubusercontent.com/Burgosa2020/tidyverse/main/edibnb-badnames.csv",
                             col_names = c("id", "price", 
                                           "neighbourhood", "accommodates",
                                           "bathroom", "bedroom", 
                                           "bed", "review_scores_rating", 
                                           "n_reviews", "url"))
names(edibnb_col_names)


```

```{r}
edibnb_clean_names <- read_csv("https://raw.githubusercontent.com/Burgosa2020/tidyverse/main/edibnb-badnames.csv") %>%
  janitor::clean_names()
names(edibnb_clean_names)
```

## Variable Types

```{r}
read_csv("https://raw.githubusercontent.com/Burgosa2020/tidyverse/main/df.csv")
read_csv("https://raw.githubusercontent.com/Burgosa2020/tidyverse/main/df.csv", 
         na = c("", "NA", ".", "9999", "Not applicable"))
```

```{r}
read_csv("https://raw.githubusercontent.com/Burgosa2020/tidyverse/main/df.csv", col_types = list(col_double(), 
                                            col_character(), 
                                            col_character()))
```

## Case Studies
#Whole section not working
ARIELY FIX IT LATER ON PLEASE
```{r}
fav_food <- read_csv("https://raw.githubusercontent.com/Burgosa2020/tidyverse/main/favourite-food.csv")
fav_food


fav_food <- read_csv("https://raw.githubusercontent.com/Burgosa2020/tidyverse/main/favourite-food.csv") %>%
  janitor::clean_names()
fav_food
```
# Not working

fav_food <- read_excel("data/favourite-food.xlsx",
                       na = c("N/A", "99999")) %>%
  janitor::clean_names()
fav_food
## Making age numeric
fav_food <- fav_food %>%
  mutate(
    age = if_else(age == "five", "5", age),
    age = as.numeric(age)
    )
glimpse(fav_food)

fav_food %>%
  count(ses)
  
  ## Make **ses** factor
  
  fav_food <- fav_food %>%
  mutate(ses = fct_relevel(ses, "Low", "Middle", "High"))
fav_food %>%
  count(ses)
  
  ### Put Together
  
  av_food <- read_excel("data/favourite-food.xlsx", na = c("N/A", "99999")) %>%
  janitor::clean_names() %>%
  mutate(
    age = if_else(age == "five", "5", age), 
    age = as.numeric(age),
    ses = fct_relevel(ses, "Low", "Middle", "High")
  )
fav_food

```

## Out and Back
 #fix top before continuing 
```(r)
write_csv(fav_food, file = "https://raw.githubusercontent.com/Burgosa2020/tidyverse/main/fav-food-clean.csv")
fav_food_clean <- read_csv("https://raw.githubusercontent.com/Burgosa2020/tidyverse/main/fav-food-clean.csv")
```
 

